Federated Learning's Blessing:\\ FedAvg has Linear Speedup

### 2020-06-10 source/app_sumarization.tex
Update app_sumarization.tex

In~\cite{haddadpour2019convergence}, they also provide $\cO(1/NT)$ convergence rate of non-convex problems under Polyak-Łojasiewicz (PL) condition, which
means their results can directly apply to the strongly convex problems. However, their assumption is based on bounded gradient diversity, defined as follows: 
\begin{align*}
	\Lambda(\vw) = \frac{\sum_{k}p_{k}\|\nabla F_{k}(\mathbf{w})\|_{2}^{2}}{\|\sum_{k}p_{k}\nabla F_{k}(\mathbf{w})\|_{2}^{2}} \leq B
\end{align*} 
This is a more restrictive comparing to assuming bounded gradient under the case of target accuracy $\epsilon \rightarrow 0$ and PL condition.
To see this, consider the gradient diversity at the global optimal $\vw^*$,i.e., $\Lambda(\vw^*) = \frac{\sum_{k}p_{k}\|\nabla F_{k}(\mathbf{w})\|_{2}^{2}}{\|\sum_{k}p_{k}\nabla F_{k}(\mathbf{w})\|_{2}^{2}}$. For $\Lambda(\vw^*)$ to be bounded, it requires $\|\nabla F_{k}(\mathbf{w}^*)\|_{2}^{2} = 0$, $\forall \ k$. This indicates 
$\vw^*$ is also the minimizer of each local objective, which contradicts to the practical setting of heterogeneous data. Therefore, their bound 
is not effective for arbitrary small $\epsilon$-accuracy under general heterogeneous data while our convergence results still hold in this case.
% If we only consider the domain $\vw \in \{\vw | \|\sum_{k}p_{k}\nabla F_{k}(\mathbf{w})\|_{2}^{2} > c\}$, where $c$ is a positive constant. 
% The bounded gradient can imply gradient diversity (see Corollary 10 in ~\cite{li2018federated}). In this case, the gradient diversity is a relaxed

>>>>

In~\cite{haddadpour2019convergence}, they also provide $\cO(1/NT)$ convergence rate of non-convex problems under Polyak-Łojasiewicz (PL) condition, which
means their results can directly apply to the strongly convex problems. However, their assumption is based on bounded gradient diversity, defined as follows: 
\begin{align*}
	\Lambda(\vw) = \frac{\sum_{k}p_{k}\|\nabla F_{k}(\mathbf{w})\|_{2}^{2}}{\|\sum_{k}p_{k}\nabla F_{k}(\mathbf{w})\|_{2}^{2}} \leq B
\end{align*} 
This is a more restrictive assumption comparing to assuming bounded gradient under the case of target accuracy $\epsilon \rightarrow 0$ and PL condition.
To see this, consider the gradient diversity at the global optimal $\vw^*$, i.e., $\Lambda(\vw^*) = \frac{\sum_{k}p_{k}\|\nabla F_{k}(\mathbf{w})\|_{2}^{2}}{\|\sum_{k}p_{k}\nabla F_{k}(\mathbf{w})\|_{2}^{2}}$. For $\Lambda(\vw^*)$ to be bounded, it requires $\|\nabla F_{k}(\mathbf{w}^*)\|_{2}^{2} = 0$, $\forall \ k$. This indicates 
$\vw^*$ is also the minimizer of each local objective, which contradicts to the practical setting of heterogeneous data. Therefore, their bound 
is not effective for arbitrary small $\epsilon$-accuracy under general heterogeneous data while our convergence results still hold in this case.
% If we only consider the domain $\vw \in \{\vw | \|\sum_{k}p_{k}\nabla F_{k}(\mathbf{w})\|_{2}^{2} > c\}$, where $c$ is a positive constant. 
% The bounded gradient can imply gradient diversity (see Corollary 10 in ~\cite{li2018federated}). In this case, the gradient diversity is a relaxed
